Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-07 demystify.tex

\paragraph{Response Deadlines} Accepted students are usually given a deadline to make decision on their offers, often around around \textbf{April 15th} in the US. This is a standard deadline for PhD programs due to the Council of Graduate Schools (CGS) Resolution (\href{https://cgsnet.org/wp-content/uploads/2024/01/CGS_April15_Resolution_Jan312024.pdf}{see more}). After this date, CS programs can gauge how many slots remain unfilled.

@@

\paragraph{Rejection Letters} Typically, schools start sending out rejection letters to remaining applicants after they have finalized their admissions decisions. Thus, rejection letters are often sent out late (e.g., after April 15th or even much later). Not much you can do here, you can try to contact the school to ask about your status, but they might not reply, they might say they are still reviewing applications, or give you inaccurate information (e.g., you will hear in two weeks -- which might not happen). In short, you just have to wait.

>>>>

\paragraph{Response Deadlines} Accepted students are usually given a deadline to make decision on their offers, often around \textbf{April 15th} in the US. This is a standard deadline for PhD programs due to the Council of Graduate Schools (CGS) Resolution (\href{https://cgsnet.org/wp-content/uploads/2024/01/CGS_April15_Resolution_Jan312024.pdf}{see more}. After this date, CS programs can gauge how many slots remain unfilled.

@@

\paragraph{Rejection Letters} Typically, schools start sending out rejection letters to remaining applicants after they have finalized their admissions decisions. Thus, rejection letters are often sent out late (e.g., after April 15th or even much later). Not much you can do here, you can try to contact the school to ask about your status, but they might not reply, they might say they are still reviewing applications, or give you inaccurate information (e.g., you will hear in two weeks). In short, you just have to be patient and wait.
